Expand 
\begin{enumerate}[label=\thesubsection.\arabic*, ref=\thesubsection.\theenumi,itemsep=1ex]
	\begin{multicols}{4}
\item $\brak{x^2+\frac{3}{4}}^4, x \neq 0$.
\item $\brak{1-2x}^5$
\item $\brak{\frac{2}{x} - \frac{x}{2}}^5$
\item $\brak{2x - 3}^6$
\item $\brak{\frac{x}{3} + \frac{1}{x}}^5$
\item $\brak{x + \frac{1}{x}}^6$
	\end{multicols}
\end{enumerate}
Using binomial theorem, evaluate each of the following
\begin{enumerate}[label=\thesubsection.\arabic*, ref=\thesubsection.\theenumi,itemsep=1ex,resume*]
	\begin{multicols}{4}
\item $\brak{96}^3$
\item $\brak{102}^5$
\item $\brak{101}^4$
\item $\brak{99}^5$
\item $\brak{98}^5$.
\end{multicols}
\end{enumerate}
Find the coefficient of
\begin{enumerate}[label=\thesubsection.\arabic*, ref=\thesubsection.\theenumi,itemsep=1ex,resume*]
\item $x^5$ in $\brak{x+3}^8$
\item $a^5b^7$ in $\brak{a - 2b}^{12}.$
\item $x^6y^3$ in $\brak{x+2y}^9$.
\end{enumerate}
Write the general term in the expansion of
\begin{enumerate}[label=\thesubsection.\arabic*, ref=\thesubsection.\theenumi,itemsep=1ex,resume*]
\item $\brak{x^2 - y}^6$
\item $\brak{x^2 - yx}^{12}, x \neq 0.$
\end{enumerate}
Find the middle terms in the expansions of 
\begin{enumerate}[label=\thesubsection.\arabic*, ref=\thesubsection.\theenumi,itemsep=1ex,resume*]
\item $\brak{3 - \frac{x^3}{6}}^7$
\item $\brak{\frac{x}{3} + 9y}^{10}$
\item Which is larger $\brak{1.01}^{1000000}$ or 10,000?
\item Using binomial theorem, prove that $6^n-5n$ always leaves remainder 1 when divided by 25.
\item Find $a$ if the $17^{th}$ and $18^{th}$ terms of expansiom $\brak{2+a}^{50}$ are equal.
\item Show that the middle term in the expansion of $\brak{1+x}^{2n} $ is  $\frac{1.3.5 \dots \brak{2n-1}}{n!}2n x^n,$ where $n$ is a positive integer.
\item The second, third and fourth terms in the binomial expansion $\brak{x+a}^n$ are 240, 720 and 1080 respectively. Find $x,a$ and $n$.
\item The coefficients of three consecutive terms in the expansion of $\brak{1+a}^n$ are in the ratio 1:7:42. Find $n$.
\item Find the term independent of $x$ in the expansion of $\brak{\frac{3}{2}x^2 - \frac{1}{3x}}^6$.
\item If the coefficients of $a^{r-1},a^r$ and $a^{r+1}$ in the expansion of $\brak{1+a}^n$ are in arithmetic progression, prove that $n^2 - n\brak{4r+1} + 4r^2 - 2 = 0$.
\item Show that the coefficient of the middle term in the expansion of $\brak{1+x}^{2n}$ is equal to the sum of the coefficients of two middle terms in the expansion of $\brak{1+x}^{2n-1}.$
\item Find the coefficient of $a^4$ in the product $\brak{1+2a}^4\brak{2-a}^5$ using binomial theorem.
\item Find thr $r^{th}$ term from the end in the expansion of $\brak{x+a}^n.$
\item Find the term independent of $x$ in the expansion of $\brak{\sqrt[3]{x} + \frac{1}{2\sqrt[3]{x}}}^{18}, x>0$.
\item The sum of the coefficients of the first three terms in the expansion of $\brak{x - \frac{3}{x^2}}^m, x\neq0, m$ being a natural number, is 559. Find the term of the expansion containing $x^3$.	
\item If the coefficients of $\brak{r-5}^{th}$ and  $\brak{2r-1}^{th}$ terms in the expansion of $\brak{1+x}^{34}$ are equal, find $r$.


\item Using binomial theorem, indicate which number is larger $\brak{1.1}^{10000}$ or 1000.
\item Find $\brak{a+b}^4 - \brak{a-b}^4.$ Hence evaluate 
$\brak{\sqrt{3} + \sqrt{2}}^4$ - $\brak{\sqrt{3} - \sqrt{2}}^4.$
\item Find $\brak{x + 1}^6 + \brak{x - 1}^6.$ Hence or otherwise evaluate $\brak{\sqrt{2} + 1}^6 + \brak{\sqrt{2} - 1}^6.$
\item Show that $9^{n+1} - 8n - 9$ is divisible by 64, whenever $n$ is a positive integer.
\item Prove that $ \sum \limits_{r=0}^{n}\ 3^r$ $ ^nC_r\ = 4 ^n$.
\item Find the $4^{th}$ term in the expansion of $\brak{x - 2y}^{12}.$
\item Find the $13^{th}$ term in the expansion of $ \brak{9x - \frac{1}{3\sqrt{x}}}^{18}$,$ x \neq 0.$
\item In the expansion of $\brak{1 + a}^{m+n}$, prove that coefficients of $a^m$ and $a^n$ are equal.
\item The coefficients of the $\brak{r - 1}^{th}, r^{th}$ and $\brak{r + 1}^{th}$ terms in the expansion of $\brak{x + 1}^n$ are in the ratio 1 : 3: 5. Find $n$ and $r$.
\item Prove that the coefficient of $x^n$ in the expansion of $\brak{1 + x}^{2n}$ is twice the coefficient of $x^n$ in the expansion of $\brak{1 + x}^{2n - 1}.$
\item Find the positive value of $m$ for which the coefficient of $x^2$ in the expansion $\brak{1 + x}^m$ is 6.
\item Find $a, b$ and $n$ in the expansion of $\brak{a + b}^n$ if the first three terms of the expansion are 729, 7290 and 30375 respectively.
\item Find the coefficient of $x^5$ in the product $\brak{1 + 2x}^6 \brak{1 - x}^7$ using binomial theorem.
\item Find $a$ if the coefficients of $x^2$ and $x^3$ in the expansion of $\brak{3 + ax}^9$ are equal.
\item If $a$ and $b$ are distinct integers, prove that $a - b$ is a factor of $a^n - b^n$, whenever $n$ is a positive integer.
\item Evaluate $\brak{\sqrt{3} + \sqrt{2}}^6$ - $\brak{\sqrt{3} - \sqrt{2}}^6$
\item Find the value of $\brak{a^2 + \sqrt{a^2 - 1}}^4$ + $\brak{a^2 - \sqrt{a^2 - 1}}^4.$
\item Find an approximation of $\brak{0.99}^5$ using the first three terms of its expansion.
\item Find $n$, if the ratio of the fifth term from the beginning to the fifth term from the end in the expansion of $\brak{\sqrt[4]{2} + \frac{1}{\sqrt[4]{3}}}^n$ is $\sqrt{6} : 1$
\item Expand using binomial theorem $\brak{1 + \frac{x}{2} - \frac{2}{x}}^4$, $x \neq 0$.
\item Find the expansion of $\brak{3x^2 - 2ax + 3a^2}^3$ using binomial theorem.
\end{enumerate}
